---
title: "Make Datasets"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
library(lubridate)
library(anytime)
library(matlab)
library(readr)
library(stringr)
```

Define where to get the data from and where to put the resulting data sets:
```{r}
data_source_dir = "../data_raw/"
data_destination_dir = "../datasets/"
```

Define helper functions that get information from a filename:
```{r}
get_provider_by_filename = function(filename) {
  split_result = str_split(filename, "_")
  return(split_result[[1]][2])
}

# example:
get_provider_by_filename("1544519617_vodafone_ul.txt")
```

```{r}
get_datatype_by_filename = function(filename) {
  split_result = str_split(filename, "_")
  ending = split_result[[1]][3]
  split_result_ending = str_split(ending, "\\.")
  return(split_result_ending[[1]][1])
}

# example:
get_datatype_by_filename("1544519617_vodafone_ul.txt")
```

```{r}
get_start_time_by_filename = function(filename) {
  split_result = str_split(filename, "_")
  result = as_datetime(as.integer(split_result[[1]][[1]]))
  return(result)
}

# example:
get_start_time_by_filename("1544519617_vodafone_ul.txt")
```

This function creates a dataset for a given `datatype` like "ul", "dl", "context" or cells.
The provider is added as an extra column as well as the scenario.
```{r}
make_dataset = function(data_location, datatype) {
  
  # read all datasets and store them in a list to combine them later
  datasets = list()
  
  scenarios = c("urban", "suburban", "campus", "highway")
  for (cur_scenario in scenarios) {
    
    # get the current path where the files are located and list the files
    cur_path = str_c(data_location, "/", cur_scenario)
    data_files = list.files(cur_path)
    
    # now read each file
    for (cur_filename in data_files) {
      
      # only read when the datatype matches the one we want
      cur_datatype = get_datatype_by_filename(cur_filename)
      if (cur_datatype != datatype) {
        next
      }
      
      # read the file and add a column for the provider and for the scenario
      cur_provider = get_provider_by_filename(cur_filename)
      cur_start_time = get_start_time_by_filename(cur_filename)
      cur_dataset = read_csv(str_c(cur_path, "/", cur_filename), col_type=cols()) %>%
        mutate(scenario=cur_scenario, provider=cur_provider, start_time=cur_start_time)
      
      # attach it to the list
      datasets[[length(datasets)+1]] = cur_dataset
    }
  }
  
  # build the final dataset and convert the seconds to proper dates
  final_dataset = bind_rows(datasets) %>% 
    mutate(timestamp=as_datetime(timestamp_ms)) %>%
    arrange(start_time)
  return(final_dataset)
}
```

Now create the data sets:
```{r}
dataset_ul = make_dataset(data_source_dir, datatype="ul")
glimpse(dataset_ul)
```

```{r}
dataset_dl = make_dataset(data_source_dir, datatype="dl")
glimpse(dataset_dl)
```

```{r}
dataset_context = make_dataset(data_source_dir, datatype="context")
glimpse(dataset_context)
```

```{r}
dataset_cells = make_dataset(data_source_dir, datatype="cells")
glimpse(dataset_cells)
```

# Add the eNodeB-ID

This function converts a cell-ID to an eNodeB-ID:
```{r}
cell_id_to_enodeb = function(cell_id) {
  result = tryCatch(
    {
      hex_string = as.character(as.hexmode(cell_id))
      enodeb_hex = str_sub(hex_string, start=1, end=-3)
      enodeb_integer = as.integer(as.hexmode(enodeb_hex))
      return(enodeb_integer)
    },
    error = function(err) {
      return(NA)
    }
  )
  return(result)
}
```

Let's test it using the example from the slides (the correct eNodeB-ID is 50464):
```{r}
cell_id_to_enodeb(12918809)
```

A few more tests:
```{r}
print(cell_id_to_enodeb(13828122)==54016)
print(cell_id_to_enodeb(26385408)==103068)
print(cell_id_to_enodeb(13067274)==51044)
print(is.na(cell_id_to_enodeb(NA)))
print(is.na(cell_id_to_enodeb(0)))
```

Now update the datasets to also contain the eNodeB-ID:
```{r}
dataset_ul = dataset_ul %>% mutate(enodeb=map_int(ci, cell_id_to_enodeb))
dataset_dl = dataset_dl %>% mutate(enodeb=map_int(ci, cell_id_to_enodeb))
dataset_context = dataset_context %>% mutate(enodeb=map_int(ci, cell_id_to_enodeb))
dataset_cells = dataset_cells %>% mutate(enodeb=map_int(ci, cell_id_to_enodeb))
```

# Add an ID for each drive

```{r}
get_drive_ids = function(data) {
  
  num_rows = nrow(data)
  drive_ids = integer(num_rows)
  
  last_start_time_by_scenario = character(4)
  names(last_start_time_by_scenario) = c("urban", "suburban", "campus", "highway")
  
  last_drive_id_by_scenario = integer(4)
  names(last_drive_id_by_scenario) =c("urban", "suburban", "campus", "highway")
  
  for(cur_row in seq_len(num_rows)) {
    
    cur_scenario = data[[cur_row, "scenario"]]
    cur_start_time = as.character(data[[cur_row, "start_time"]])
    
    last_start_time = last_start_time_by_scenario[cur_scenario]
    last_drive_id = last_drive_id_by_scenario[cur_scenario]
    
    if (cur_start_time != last_start_time) {
      cur_drive_id = last_drive_id + 1
      drive_ids[cur_row] = cur_drive_id
      last_start_time_by_scenario[cur_scenario] = cur_start_time
      last_drive_id_by_scenario[cur_scenario] = cur_drive_id
      next()
    }
    
    drive_ids[cur_row] = last_drive_id
  }
  
  return(drive_ids)
}
```

```{r}
add_drive_ids = function(dataset) {
  
  dataset = arrange(dataset, start_time)
  
  dataset_o2 = filter(dataset, provider=="o2")
  dataset_tmobile = filter(dataset, provider=="tmobile")
  dataset_vodafone = filter(dataset, provider=="vodafone")
  
  result = bind_rows(
    add_column(dataset_o2, drive_id = factor(get_drive_ids(dataset_o2))),
    add_column(dataset_tmobile, drive_id = factor(get_drive_ids(dataset_tmobile))),
    add_column(dataset_vodafone, drive_id = factor(get_drive_ids(dataset_vodafone)))
  )
  
  return(result)
}
```

```{r}
dataset_ul = add_drive_ids(dataset_ul)
dataset_dl = add_drive_ids(dataset_dl)
dataset_context = add_drive_ids(dataset_context)
dataset_cells = add_drive_ids(dataset_cells)
```

```{r}
ggplot(
  filter(dataset_ul, timestamp<=ymd(20181211), provider=="tmobile", scenario=="campus"),
  aes(x=timestamp, y=throughput_mbits)
) + geom_point(aes(color=drive_id)) +
  geom_line(aes(color=drive_id)) +
  ggtitle("First three campus drives for tmobile (dataset_ul)")
```

<<<<<<< HEAD
```{r}
ggplot(
  filter(dataset_context, timestamp<=ymd(20181211), provider=="tmobile", scenario=="campus"),
  aes(x=timestamp, y=rsrp_dbm)
) + geom_point(aes(color=drive_id)) +
  geom_line(aes(color=drive_id)) +
  ggtitle("First three campus drives for tmobile (dataset_context)")
```

# Add Neighboring RSRP and RSRQ in Context File

```{r}
add_neighbor_info = function(dataset_context, dataset_cells) {
  
  dataset_context <- dataset_context %>% drop_na() %>% arrange(timestamp)
  dataset_cells <- filter(dataset_cells, rsrp_dbm!=0)
  
  # füge zusätzliche Spalte mit erstmal nur Nullen in context, wo dann am Ende die errechneten
  # RSRP der Nachbarzellen eingefügt werden sollen 
  dataset_context$rsrp_neighbor <- 0
  dataset_context$rsrq_neighbor <- 0
  
  for (p in c("o2", "tmobile", "vodafone")){
    
    dataset_context_p = filter(dataset_context, provider==p)
  	dataset_cells_p <- filter(dataset_cells, provider==p)
  
  	for (s in unique(dataset_context_p$scenario)){
  	  
      dataset_context_ps <- filter(dataset_context_p, scenario==s)
  		dataset_cells_ps <- filter(dataset_cells_p, scenario==s)
      		
  		for (d in unique(dataset_context_ps$drive_id)){
  		  
        dataset_context_psd <- filter(dataset_context_ps, drive_id==d)
  			dataset_cells_psd <- filter(dataset_cells_ps, drive_id==d)
  			
        for (i in 1:dim(dataset_context_psd)[1]){
          
  				if (any(dataset_cells_psd$timestamp == dataset_context_psd$timestamp[i])){
  					neighbor <- dataset_cells_psd[which(dataset_cells_psd$timestamp == dataset_context_psd$timestamp[i]),]
  	  			max_rsrp <- max(neighbor$rsrp_dbm)
  	  			dataset_context_psd$rsrp_neighbor[i] <- max_rsrp
  
  					neighbor <- dataset_cells_psd[which(dataset_cells_psd$timestamp == dataset_context_psd$timestamp[i]),]
  	  			max_rsrq <- max(neighbor$rsrq_db)
  	  			dataset_context_psd$rsrq_neighbor[i] <- max_rsrq
  				}
  				else {
  					if (any(dataset_cells_psd$timestamp < dataset_context_psd$timestamp[i])){
  						dataset_context_psd$rsrp_neighbor[i] <- dataset_context_psd$rsrp_neighbor[i-1]
  						dataset_context_psd$rsrq_neighbor[i] <- dataset_context_psd$rsrq_neighbor[i-1]
  					}
  					else {
  						dataset_context_psd$rsrp_neighbor[i] <- -Inf		
  						dataset_context_psd$rsrq_neighbor[i] <- -Inf
  					}
  				}		
        }
  			
  			dataset_context[
  			  (dataset_context$provider == p & dataset_context$scenario == s & dataset_context$drive_id == d),
  			] <- dataset_context_psd
  		}
  	}
  }
  
  return(dataset_context)
}
```

```{r}
dataset_context = add_neighbor_info(dataset_context, dataset_cells)
```

# Add Link Lifetime to Context File

```{r}
add_link_lifetime = function(dataset_context) {
  dataset_context <- dataset_context %>% drop_na() %>% arrange(timestamp)
  dataset_context$link_lifetime <- -1
  
  
  for (p in c("o2", "tmobile", "vodafone")){
    dataset_context_p = filter(dataset_context, provider==p)
  
    for (s in unique(dataset_context_p$scenario)){
      dataset_context_ps = filter(dataset_context_p, scenario==s)
      
      for (d in unique(dataset_context_ps$drive_id)){
        dataset_context_psd = filter(dataset_context_ps, drive_id==d)
  
        for (j in 1:dim(dataset_context_psd)[1]){
          diff_bildungs_ts = dataset_context_psd$time_s[dim(dataset_context_psd)[1]]
          for (i in min(j+1, dim(dataset_context_psd)[1]):dim(dataset_context_psd)[1]){
            if (dataset_context_psd$enodeb[i] != dataset_context_psd$enodeb[j]){
              diff_bildungs_ts <- dataset_context_psd$time_s[i]
              break
            }
          }
          
          dataset_context_psd$link_lifetime[j] <- diff_bildungs_ts - dataset_context_psd$time_s[j]
        }
  
        dataset_context[
          (dataset_context$provider == p & dataset_context$scenario == s & dataset_context$drive_id == d),
        ] <- dataset_context_psd
      }
    }
  }
  return(dataset_context)
}
```

```{r}
dataset_context = add_link_lifetime(dataset_context)
```

# Store the data

```{r}
write_csv(dataset_ul, str_c(data_destination_dir, "dataset_ul.csv"))
write_csv(dataset_dl, str_c(data_destination_dir, "dataset_dl.csv"))
write_csv(dataset_context, str_c(data_destination_dir, "dataset_context.csv"))
write_csv(dataset_cells, str_c(data_destination_dir, "dataset_cells.csv"))
```
